\chapter*{\Large \center Abstract}

Effective pest control has become vital in modern agriculture to maintain crop health and yield. With the growing problems caused by diverse pests such as insects, weeds, and plant diseases, the need for quick and accurate pest control solutions has never been greater. Pests can cause significant crop damage, resulting in significant decreases in both the quality and quantity of agricultural output. This not only has an impact on farmers' incomes, but it also poses a danger to global food security.
Integrated pest management (IPM) strategies utilise biological, cultural, mechanical, and chemical ways to control pest populations with little environmental effect. However, the accuracy of these methods is strongly dependent on accurate pest identification and the timely application of suitable management measures. Traditional pest detection methods, which involve professional knowledge and laboratory analysis, can be time-consuming and inaccessible to many farmers, particularly those in remote or underserved areas.

This research project aims to create a user-friendly mobile application in Flutter ( Hybrid app both for IOS and Android) for farmers that uses modern technology to speed up pest detection and control. The app provides accurate pest identification through machine learning, detailed pest information, recommended pesticides, and pest management guidance. Additionally, it integrates a decentralized payment system, enabling secure pesticide purchases globally. This comprehensive solution enables farmers to successfully manage pests, resulting in increased agricultural output and sustainability.

