\chapter{Introduction}

Agriculture began around 12,000 years ago with the transition from nomadic hunter-gatherer cultures to sedentary farming societies. Pests posed a significant obstacle to agriculture as it progressed.Early farmers used crude tactics and natural deterrents to combat a variety of pests.
Today, modern pest control combines traditional methods with innovative technology for example Integrated Pest Management (IPM), discussed in detail in Section 2, has evolved as a sustainable pest management strategy that combines biological, cultural, mechanical, and chemical strategies to manage pest populations while minimising environmental effects. However, the effectiveness of IPM strategies heavily relies on accurate pest identification and the timely application of control measures
(\cite{wikipediacontributors_2019_history}).

Modern technology has made it simpler to access mobile devices and the internet. Using advanced techniques like machine learning and mobile cameras, farmers can quickly identify pests. Large Language Models (LLMs) can provide detailed information about the pests and recommend appropriate pesticides. This project leverages these technologies to create a user-friendly mobile app that identifies pests, provides pesticide recommendations, and integrates blockchain technology for secure and easy purchase of recommended pesticides. This comprehensive solution enhances pest management efficiency, accessibility, and sustainability for farmers.



\section{Aims and Objectives}

This project aims to develop a hybrid application that can run on Android, iOS, and web browsers. The system allows users to upload an image of a pest found on their farm, provides details on how to handle the pest, and recommends pesticides if the pest is hazardous. This comprehensive application uses cutting-edge technology to improve farmers' pest management efficiency and accessibility.

\section{Overview of the Report}

This dissertation is contains 7 chapters. 
\begin{itemize}
    \item Chapter 1 introduces the project background, objectives, and structure of the dissertation.
    \item Chapter 2 explores the literature on the importance of pest control, causes of pests, techniques to control them, comparisons of existing apps, and the tools and technology used in the dissertation.

\end{itemize}